### 2020-07-01 evaluation.tex
fig

\section{Evaluation \& Case Study}
\label{sec-evaluation}

We evaluate the ability of the network model, testing its performance in different training and testing conditions. We perform the following experiments with two phones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras, the telephoto camera(which we use in the experiments) possessing up to 5x optical zooming ability which we will utilize fully in our experiments. 
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Figure~\ref{fig-control} and Figure~\ref{fig-control2}). Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. The model with traditional lenses(without optical zoom) is trained and tested at 1~2 meters range, while the one with optical zoom at 5~7.5 meters, at which distance less than 5\% of the characters(only the simplist ones) can be recognized by humans from the photos without the assistance of SR algorithms. The model can achieve an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
In the optical zoom group the accuracy of the model dropped drastically at 7m distance. Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes,etc.). It's the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixelwize error rises steadily with the increased distance, the accuracy will experience a drastic drop.

\begin{figure*}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control2}}
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
    \hfill
    \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
    \label{fig-performance-1}
\end{figure*}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table1.pdf}
%     \caption{Performance in Controlled Environment(Traditional Lenses)}
%     \label{fig-control}
% \end{figure}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
%     \caption{Performance in Controlled Environment(Optical Zoom Lenses)}
%     \label{fig-control2}
% \end{figure}
\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random} and Figure~\ref{fig-random-2}). The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table2.pdf}
%     \caption{Performance in Random Environment(Traditional Lenses)}
%     \label{fig-random}
% \end{figure}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/distance2.pdf}
%     \caption{Performance in Random Environment(Optical Zoom Lenses)}
%     \label{fig-random-2}
% \end{figure}
We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability. Also, the model performs better at closer distances. As the model is trained initially on the 5m group data, it performs especially well at this distance, while the accuracy at other distances experience certain levels of decrease. Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplest characters can escape from being flooded by noise.

\begin{figure*}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
    \hfill
    \caption{Performance for Adapting Ability and various processing images.}
    \label{fig:adapting}
\end{figure*}

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments. The results are shown in Figure~\ref{fig-adapt-tranditional}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table3.pdf}
%     \caption{Adapting Ability(Traditional Lenses)}
%     \label{table-adapt}
% \end{figure}

@@

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level averageing. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noized and deformed patterns, while VideoSR approaches rely apon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing. The results are shown in Figure~\ref{table-comp}.

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table4.pdf}
%     \caption{Comparison with other architectures}
%     \label{table-comp}
% \end{figure}

\begin{table}[!t]
    \centering
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR(db) & 13.32 & 7.69 & 8.403\\ 
    OCR Accuracy(\%) & 100 & 10 & 23\\ \bottomrule
    \end{tabular}
    \caption{Comparison with existing systems.}
    \label{table-comp}
\end{table}

@@

\begin{table}[!t]
    \centering
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & Home & Transport & Theater \\ \midrule
    Baseline & 5 & 0 & 0\\ 
    \midrule
    OCR & 100 & 10 & 23\\ 
    Human & 95 & 85 & 70\\ \bottomrule
    \end{tabular}
    \caption{Recognition accuracy in various scenarios.}
    \label{table-scenarios}
\end{table}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
%     \caption{Accuracy in different real-life scenarios}
% 	\label{table-accuracy}
% \end{figure}

@@

\begin{table}[!t] 
    \centering
    \begin{tabular}{ccccc}
        \toprule
    System & None & Camera & Target & Both  \\
    \midrule
    Baseline & 5 & 0 & 5& 5\\ 
    \midrule
    OCR & 95 & 85 & 80 & 80\\ 
    Human & 95 & 85 & 80 & 85\\ \bottomrule
    \end{tabular}
    \caption{Impact of hand tremors while holding various items.}
    \label{table-tremor}
\end{table}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
% \caption{Influence of hand tremors}
% \label{table-tremor}
% \end{figure}

@@

>>>>

\section{Evaluation \& Case Study}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the ability of the network model, testing its performance in different training and testing conditions. We perform the following experiments with two phones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras, the telephoto camera(which we use in the experiments) possessing up to 5x optical zooming ability which we will utilize fully in our experiments. 
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}). Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. The model with traditional lenses(without optical zoom) is trained and tested at 1~2 meters range, while the one with optical zoom at 5~7.5 meters, at which distance less than 5\% of the characters(only the simplist ones) can be recognized by humans from the photos without the assistance of SR algorithms. The model can achieve an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
\begin{figure}[!t]
    \centering
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
    \hfill
    \caption{Performance in Controlled Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

In the optical zoom group the accuracy of the model dropped drastically at 7m distance. Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes,etc.). It's the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixelwize error rises steadily with the increased distance, the accuracy will experience a drastic drop.

\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}). The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses. 
\begin{figure}[!t]
    \centering
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
    \hfill
    \caption{Performance in Random Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability. Also, the model performs better at closer distances. As the model is trained initially on the 5m group data, it performs especially well at this distance, while the accuracy at other distances experience certain levels of decrease. Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplest characters can escape from being flooded by noise.

% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
%     \hfill
%     \caption{Performance for Adapting Ability and various processing images.}
%     \label{fig:adapting}
% \end{figure*}

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments. The results are shown in Figure~\ref{fig-adapt-tranditional}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
\begin{figure}[!t]
    \centering
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
    \hfill
    \caption{Performance for Adapting Ability using Traditional Lens and Optical Lens.}
    \label{fig:adapting}
\end{figure}

@@

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level averageing. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noized and deformed patterns, while VideoSR approaches rely apon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing. The results are shown in Figure~\ref{table-comp}.
\begin{table}[!t]
    \centering
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR(db) & 13.32 & 7.69 & 8.403\\ 
    OCR Accuracy(\%) & 100 & 10 & 23\\ \bottomrule
    \end{tabular}
    \caption{Comparison with existing systems.}
    \label{table-comp}
\end{table}

@@

\begin{table}[!t]
    \centering
    \begin{tabular}{@{}cccc@{}}
        \toprule
    Scenarios & Home & Transport & Theater \\ \midrule
    Baseline & 5 & 0 & 0\\ 
    \midrule
    OCR & 100 & 10 & 23\\ 
    Human & 95 & 85 & 70\\ \bottomrule
    \end{tabular}
    \caption{Recognition accuracy in various scenarios.}
    \label{table-scenarios}
\end{table}

@@

\begin{table}[!t] 
    \centering
    \begin{tabular}{ccccc}
        \toprule
    Items & None & Camera & Target & Both  \\
    \midrule
    Baseline & 5 & 0 & 5& 5\\ 
    \midrule
    OCR & 95 & 85 & 80 & 80\\ 
    Human & 95 & 85 & 80 & 85\\ \bottomrule
    \end{tabular}
    \caption{Impact of hand tremors while holding various items.}
    \label{table-tremor}
\end{table}

@@

\begin{figure}[!t]
    \centering
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
    \hfill
    \caption{Performance with various processing images using Traditional Lens and Optical Lens.}
    \label{fig:adapting}
\end{figure}
